Fast approximate Bayesian inference of HIV indicators using PCA adaptive Gauss-Hermite quadrature

### 2025-08-12 src/docs_paper-jtb/paper.Rmd
Correction to figure caption

(ref:us-alpha-xs) The parameters `us_alpha_xs` had the greatest difference in KS test statistics between GEB and GPCA-AGHQ to NUTS. This figure shows the element ``r paste0(ui_lambda_x$par)``. For this element, the NUTS potential scale reduction factor was `r ui_lambda_x$rhat` and effective sample size was `r ui_lambda_x$ess`.

>>>>

(ref:us-alpha-xs) The parameters `us_alpha_xs` had the greatest difference in KS test statistics between GEB and GPCA-AGHQ to NUTS. This figure shows the element ``r paste0(us_alpha_xs$par)``. For this element, the NUTS potential scale reduction factor was `r us_alpha_xs$rhat` and effective sample size was `r us_alpha_xs$ess`.
